A weakly structured stem for human origins in Africa

### 2022-01-11 paper.tex
add continuous migration with isolated stems
minor update to fig 4
add fig3 and captions

\documentclass[]{article}
\usepackage[super,numbers]{natbib}

@@

Allowing for continuous migration between the stem populations substantially
improved the fits relative to zero migration ($LL \approx -102,600$ vs.
$-107,700$ in the merger scenario and $LL \approx -115,500$ vs. $-128,000$ with
continuous migration). With continuous migration between stems, population
structure extends back to 1.1--1.4Mya (Table~\ref{tab:migration-rates}).
Migration between the stems in these models is moderate, with a fraction of
migrant lineages each generation estimated as
$m=6.43\times10^{-5}-1.16\times10^{-4}$. For comparison, this roughly compares
to inferred migration rates between connected contemporary populations over the
past 50kya (Table~\ref{tab:migration-rates}). This ongoing (or at least,
periodic) gene flow qualitatively distinguishes these models from previously
proposed archaic admixture models (Figure~\ref{fig:supp-possible-models}C) as
the early branches remain closely related (Figure 3).

@@

\begin{figure}[t!]
    \centering
    %\includegraphics{figures/fig3.pdf}
    \caption{
        \textbf{fig3}
    }
    \label{fig:3}
\end{figure}

@@

@@

\begin{figure}[ht!]
    \centering
    \includegraphics{figures/fig4}
    \caption{fig4}
    \label{fig:4}
\end{figure}

>>>>

\documentclass{article}
\usepackage[super,numbers]{natbib}

@@

Allowing for continuous migration between the stem populations substantially
improved the fits relative to zero migration ($LL \approx -102,600$ vs.
$-107,700$ in the merger scenario and $LL \approx -115,500$ vs. $-126,600$ with
continuous migration). With continuous migration between stems, population
structure extends back to 1.1--1.4Mya (Table~\ref{tab:migration-rates}).
Migration between the stems in these models is moderate, with a fraction of
migrant lineages each generation estimated as
$m=6.43\times10^{-5}-1.16\times10^{-4}$. For comparison, this roughly compares
to inferred migration rates between connected contemporary populations over the
past 50kya (Table~\ref{tab:migration-rates}). This ongoing (or at least,
periodic) gene flow qualitatively distinguishes these models from previously
proposed archaic admixture models (Figure~\ref{fig:supp-possible-models}C) as
the early branches remain closely related (Figure 3).

@@

\begin{figure}[t!]
    \centering
    \includegraphics{figures/fig3.pdf}
    \caption{
        \textbf{Predicted population structure over time.}
        From the best fit models of our two parameterizations (top row:
        continuous migration, bottom row: multiple merger), we computed
        preditions of population structure between contemporaneous populations
        over time ($F_{ST}$) and the proportion of drift between pairs of sampled
        populations that aligns with drift between populations in the past
        ($\alpha^2$).
    }
    \label{fig:3}
\end{figure}

@@

\begin{figure}[ht!]
    \centering
    \includegraphics{figures/fig4}
    \caption{
        \textbf{Model validation using independent statistics.} (A--C) Using
        our best fit models to the LD and pairwise diversity statistics, we
        simulated expected conditional site-frequency-spectra (cSFS) and
        compared to the observed cSFS from the data. Our inferred models
        provide a good fit to the data, even though these were not used in our
        inference. Across the three populations, ancestral state
        misidentification was consistently inferred to be 1.5--1.7\% for
        intergenic loci (Supp. Methods). (D, E) We used Relate
        \citep{Speidel2019-nj} to reconstruct genome-wide gene genealogies,
        which we used to estimate coalescence rate trajectories. While
        coalescence rate distributions are informative statistics about past
        evolutionary processes, interpretation can be hindered by migration and
        population structure. Translating relative cross-coalescence curves
        into population divergences is especially prone to misinterpretation.
    }
    \label{fig:4}
\end{figure}

@@
